### 2010-06-30 trunk/paper/IIWAS2010/content/system_arch.tex
latest

Morpheus uses an ontology that contains categories of a particular realm of interest. Every leaf node in the ontology is associated with a corpus of words belonging to a category.  For example, we have constructed an automotive ontology containing categories relevant to the automotive realm. This ontology provides a structure for reference in the following sections.

%% Comment made by Joir-dan (2010-06-29)
 %%Need to remove any references to Markov Blanket... since we abandoned that ship a while ago...

Morpheus uses the DBpedia categories, Wikipedia pages and the WordNet synset heterarchy to construct ontologies. This approach is motivated by YAGO \cite{Suchanek2009phd}. First a realm is mapped to a DBpedia category \cite{Bizer2009}. 
Then a \emph{Markov Blanket} \cite{PRIS} is created covering all neighboring categories and using the DBpedia ontology properties \emph{broader} and \emph{narrower}. From here, the system recursively includes all categories up to the root.

%% ^^^ Needs to remove references to blanket

Once we have the categories belonging to a particular realm, we associate them with WordNet synsets using an approach similar to YAGO\cite{Suchanek2009phd}. We determine a \emph{head noun} in the category name and search for it in the WordNet synsets. DBpedia categories having no WordNet synset match are excluded from our ontology.

To build a corpus for each of the leaf nodes in the ontology, 
we extract \emph{terms} from the Wikipedia pages associated with the 
the DBpedia categories. From this term corpus, 
we can find the likelihood of a term belonging to a particular category. This assists in categorizing terms in a \emph{path-follower} query.
The likelihood is determined by the probability of a category given a term 
using \textit{Bayes Rule} (Eq. \ref{eq:bayesrule}), since we can 
easily obtain the term-category and term-corpus probabilities as 
relative frequencies.

%% Comment by Joir-dan 2010-06-30: Term should prolly be replaced by n-gram

@@

Queries inserted by path-followers take a different approach. The Morpheus search system parses, tags, and processes the queries in order to pull important n-grams. The system then assigns the most probable realm to the query using \textit{realm}|\textit{n-gram} priors calculated from realm-specific corpora. Once the realm is assigned, an ontology search is performed to assign classes to the n-grams. An SSQ is constructed and the system attempts to match this SSQ to a query path created by a path-finding user. Rather than matching n-grams, the goal is to match input and output classes, since the paths can potentially answer similar queries.

@@

To answer a user's query, a \textit{candidate
SSQ}, Morpheus finds similar SSQs that belong to QRMs in the Morpheus data store (a \textit{qualified SSQ}). We need a similarity measure to match the candidate SSQ
with a qualified SSQ. For the SSQ similarity, we
consider the SSQ components such as query-realm, input
terms and output terms, and their assigned categories or classes [To be changed]. The,
\textit{category divergence} of two categories characteristics their 
similarity based on an ontology class heterarchy. 
It is motivated by the concept of multiple
dispatch in CLOS and Dylan programming for generic function \emph{type} matches.

We consider the category match as a type match and we use 
\emph{category divergence} to calculate the relevance between 
the candidate SSQ and a qualified SSQ. Each qualified SSQ will 
have input terms, output terms, and associated classes, and one realm (from QRM). 
For the candidate SSQ, the relevant categories for terms 
are determined from the NLP engine and corpora. The calculation of a realm 
for a candidate query is done using the n-grams found within said query 
and the probabilities (if any) found using frequencies within the database.
We match QRMs that belong to the same \emph{realm} of the candidate SSQ. 
The relevance of a qualified SSQ to the candidate SSQ is 
determined by aggregating the divergence measure of input-term-categories 
associated with them. In addition, we order QRMs in the data store 
by decreasing relevance. The order provides a ranking for the results 
to the user. The following subsection describes \emph{category divergence} 
in detail.

\subsubsection{Catgeory Divergence}
\label{sec:ctd}

@@

 The evaluation of this script by the QRE simulates the behavior of a human browsing the web, that is, clicking buttons to follow links, submitting forms, and highlighting of data to form a text answer.  The QRE assumes that becuase of the auto generated nature of deep web pages, the location of answers are the same irrespective of page changes.  It uses the relative XPath location to the answer node on HTML pages as described in \cite{Badica06}.

>>>>

Morpheus uses an ontology that contains classes of a particular realm of interest. Each leaf node in the ontology is associated with a corpus of words belonging to a class.  For example, we have constructed an automotive ontology containing classes relevant to the automotive realm. This ontology provides a structure for reference in the following sections.

%% Need ontology paragraph

Morpheus uses the DBpedia categories, Wikipedia pages, and the WordNet synset heterarchy to find class-relevant web pages. This approach is motivated by YAGO \cite{Suchanek2009phd}. First a realm is mapped to a DBpedia category \cite{Bizer2009}. Then a \emph{Markov Blanket} \cite{PRIS} is created covering all neighboring categories and using the DBpedia ontology properties \emph{broader} and \emph{narrower}.

To build a corpus for each of the leaf nodes in the ontology, we extract \emph{terms} from the Wikipedia pages associated with the DBpedia categories found in its blanket. From this term corpus, we can find the likelihood of a term belonging to a particular category. This assists in categorizing terms in a \emph{path-follower} query. The likelihood is determined by the probability of a category given a term using \textit{Bayes Rule} (Eq. \ref{eq:bayesrule}), since we can easily obtain the term-category and term-corpus probabilities as relative frequencies.

%Once we have the categories belonging to a particular realm, we associate them with WordNet synsets using an approach similar to YAGO. We determine a \emph{head noun} in the category name and search for it in the WordNet synsets. DBpedia categories having no WordNet synset match are excluded from our ontology. <--- by Gordon

@@

Queries inserted by path-followers take a different approach. The Morpheus search system parses, tags, and processes the queries in order to pull important n-grams. The system then assigns the most probable realm to the query using $p(realm|n-gram)$ priors calculated from realm-specific corpora. Once the realm is assigned, an ontology search is performed to assign classes to the n-grams. An SSQ is constructed and the system attempts to match this SSQ to a query path created by a path-finding user. Rather than matching n-grams, the goal is to match input and output classes, since the paths can potentially answer similar queries.

@@

To answer a user's query, a \textit{candidate
SSQ}, Morpheus finds similar SSQs that belong to QRMs in the Morpheus data store (a \textit{qualified SSQ}).  To determine SSQ similarity, we
consider the SSQ's realm, input terms, output terms, and their assigned classes.

The \emph{class divergence} of two classes within the ontology characterizes their similarity.  This solution is motivated by the concept of multiple dispatch in CLOS and Dylan programming for generic function type matches.

We consider the category match as a type match and we use \emph{category divergence} to calculate the relevance between the candidate SSQ and a qualified SSQ. Each qualified SSQ will have input terms, output terms, and associated classes, and one realm (from the QRM). 
For the candidate SSQ, the relevant categories for terms are determined from the NLP engine and corpora. The calculation of a realm for a candidate query is performed using the n-grams found within the query and any probabilities as found with $p(realm|n\-gram)$. %% TODO - specify freq and reference joirdans stuff in section 3.2
We match QRMs that belong to the same realm of the candidate SSQ. The relevance of a qualified SSQ to the candidate SSQ is determined by aggregating the divergence measure of input term classes associated with each SSQ. In addition, we order QRMs in the data store 
by decreasing relevance. The order provides a ranking for the results 
to the user. The following describes \emph{category divergence} 
in detail.

%\subsubsection{Catgeory Divergence}
%\label{sec:ctd}

@@

 The evaluation of this script by the QRE simulates the behavior of a human browsing the web, that is, clicking buttons to follow links, submitting forms, and highlighting of data to form a text answer.  The QRE assumes that because of the auto generated nature of deep web pages, the location of answers are the same irrespective of page changes.  It uses the relative XPath location to the answer node on HTML pages as described in \cite{Badica06}.
